### 2020-08-28 serial.tex
update

The dynamics of the serial-interval distribution depends heavily on the joint distribution between incubation periods and generation intervals.
Here, we use a bivariate lognormal distribution to model the joint probability distribution of the intrinsic incubation periods and the intrinsic generation intervals while allowing for the possibility that they might be correlated.
Given that the viral load of SARS-CoV-2 peaks around the time of symptom onset, we generally expect the generation intervals to be positively correlated with the incubation period;
that is, individuals who develop symptoms later are more likely to transmit later.
The marginal lognormal distributions are parameterized based on parameter estimates for COVID-19 (Table 1).
We use a bivariate lognormal distribution to model the joint probability distribution of the intrinsic incubation periods and the intrinsic generation intervals while allowing for the possibility that they might be correlated.
For simplicity, we consider three values for the correlation coefficients (on the log scale) of the bivariate lognormal distribution: $\rho = -0.5, 0, 0.5$.

>>>>

The dynamics of the serial-interval distribution depends heavily on the joint distribution between incubation periods and generation intervals.
Here, we use a bivariate lognormal distribution to model the joint probability distribution of the intrinsic incubation periods and the intrinsic generation intervals while allowing for the possibility that they might be correlated.
Given that the viral load of SARS-CoV-2 peaks around the time of symptom onset, we generally expect the generation intervals to be positively correlated with the incubation period;
that is, individuals who develop symptoms later are more likely to transmit later.
Marginal distributions of incubation periods and generation intervals are parameterized based on parameter estimates for COVID-19 (Table 1).
For simplicity, we consider three values for the correlation coefficients (on the log scale) of the bivariate lognormal distribution: $\rho = -0.5, 0, 0.5$.
